---
title: "Problem Set 7"
author: "David Rügamer, Julia Terhart, Philipp Kopper"
date: "02 June 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = FALSE)
```

# Resources

1) Read chapter 27 on `Rmarkdown` in [R4DS](https://r4ds.had.co.nz/r-markdown.html).

2) Read through the slides on `Git`.

3) Read at least chapters 1-12 in [Happy Git with R](https://happygitwithr.com/).
Make sure that you make Git work on your computer and in `RStudio`. 
This is a __very__ significant task!
We will relie on `Git` very much for the rest of the semester.
Setting up `Git` may be an awful procedure but we relie on you to stay brave and work your own way through the guide.
We can literally add nothing to what is written in the guide how to set it up conveniently.

4) Optionally, complete the Datacamp Units provided on the moodle page for this topic.

5) Read the whole problem set before starting work on it.

# RMarkdown

From now on we expect you to hand in your assignments as `Rmarkdown` files.
We uploaded a template on the Moodle page which you can use.
Always provide on `knitted` (PDF or html) version and the code via `.Rmd`.

1) We attached a a very short `Rmd` file to the material of this week (lm.Rmd).
Try to knit it. 
You'll find that there are some errors.
Debug the markdown until there is no error anymore and the document looks nice.
Work in the `.Rmd` directly and _push_ it once you are done (see below).

2) We attached a PDF to the material of this week (pem.pdf). 
Try to recreate the document with the use of `Rmarkdown`, `R` and `Latex` code.

# Git

We set up a Github classroom for this class.
You find it [here](https://classroom.github.com/classrooms/65912838-classroom).
In the next weeks, we will exclusively share code there.
Getting familiar with `Github` is time consuming.
If everything goes right, it will suffice to use the following workflow to make changes for your projects when you work as an individual:

- `git add -A`

- `git commit -m"your commit message"`

- `git push`

(Of course you can achieve this also by the visual editor.)

1) Have a look at the [repo for today](https://github.com/Statistische-Software-2020/PS7-Git)
Philipp and Julia have been working on a research project together.
David, as their boss, wants to know who contributed which parts of the code.
Help David (please do not e-mail David) by answering the following questions:

- Who is responsible for which functions?

- Who contributed more to the code?

- Who pushed more often?

- Do the two have a different style?

2) Hand in this problem set via the [Github classroom assignment](https://classroom.github.com/a/3dTXLLKc):

We expect three files from you:

- The filled skeleton for `pem_answer.Rmd`

- The corrected file `lm.Rmd`

- The filled skeleton for `git.Rmd`

If meaningful also provide the knitted (PDF or html) document.

```{r}
sessionInfo()
```

You can hand in this problem set by the 8th of June in order to receive feedback.
